Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-20 manuscript.Rmd
Updated scopus files.

```{r plotSmallMultiples, cache=TRUE}
# Remove 2014 & 2015

@@

# Read Scopus database
scopus.df <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus.csv")

@@

>>>>

```{r plotSmallMultiples, cache=FALSE}
# Remove 2014 & 2015

@@

# Read Scopus database
scopus.df <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus.csv")
scopus.df2 <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus_OldHarvest.csv")

scopus.df$Year <- as.numeric(scopus.df$Year)
scopus.df <- filter(scopus.df, Year <= 2013)

@@

 ldata <- na.omit(ldata)
